Stack Safety as a Security Property

### 2021-03-01 main.tex
Add lazy and other updates

Alongside integrity, we have {\em confidentiality}, in which callers' data is protected
from leakage by their callees. Consider the first example in figure \ref{fig:confexamples},
in which {\tt main} recieves a key, then calls {\tt f}. If {\tt f} is an untrusted function,
it would be bad if it could just read {\tt key}. But there are more subtle examples,
such as the second one, where a secret value controls which function of {\tt g} and
{\tt h} are called prior to calling {\tt f}. Here, if {\tt g} or {\tt h} leaves behind
identifying information in unused stack space, {\tt f} could still deduce information
about the secret. So our confidentiality properties also support a {\em transparency rule},
that each function's behavior is independent of the state of its caller, other than arguments.
This also makes it easier, though not trivial, to prove idempotence: the channels through
which a callee can remember its own history are limited to those outside the stack.

@@

The step function of the machine takes a machine state and produces a
pair of a machine state and an {\em observation}, which may be either
silent (written \(\tau\)) or a word of data\ifaftersubmission\bcp{This is a rather concrete
  choice!  Why not leave the set of observations abstract?}\fi that the machine
communicates to the outside world:
%
\[\obs \in \OBSS = \{\tau\} \uplus \WORDS\]
\[\mach \stepstoobs{\obs} \mach' \in \MACHS \rightarrow \MACHS \times \OBSS \]
%
This step function is total, so the machine's execution traces
(defined in \cref{sec:traces}) are infinite.

@@

\judgmenttwo{\(\mach \stepstoobs{\obs} \mach'\)}{\((\mach, \pol)
               \polstep \pol'\)}
            {\(\mpstate{\mach}{\pol} \stepstopol{\obs}
               \mpstate{\mach'}{\pol'}\)}

@@

The ``trace-of'' operator, written \(\mach \hookrightarrow \machT\),
coinductively relates a machine state with the trace of machine states
and observations produced by repeated application of step. It's defined in
terms of a coinductive helper, \(\mathit{obs-forward}\):

\judgmenttwo{\(\mach \stepstoobs{\obs'} \mach'\)}
            {\(\mathit{obs-forward} ~ \mach' ~ \obs' = \machT\)}
            {\(\mathit{obs-forward} ~ \mach ~ \obs = (\mach,\obs) \machT\)}%
%
\judgment{\(\mathit{obs-forward} ~ \mach ~ \tau = \machT\)}
         {\(\mach \hookrightarrow \machT\)}
\noindent
(We use juxtaposition of an element and a sequence to represent ``cons.'')
Since the step function is total, if \(\mach \hookrightarrow \machT\),
then \(\machT\) must be infinite.

@@

\judgment{\(\neg \exists \pol' . \mpcstate{\mach}{\pol} \polstep \pol'\)}
         {\(\mathit{obs-forward} ~ \mpcstate{\mach}{\pol}{\context} ~ \obs =
           \mpcstate{\mach}{\pol}{\context},\obs\)}
%
\judgmenttwo{\(\mpcstate{\mach}{\pol}{\context} \stepstoobs{\obs'} \mpcstate{\mach'}{\pol'}{\context'}\)}
            {\(\mathit{obs-forward} ~ \mpcstate{\mach'}{\pol'}{\context'} ~ \obs' = \machT\)}
            {\(\mathit{obs-forward} ~ \mpcstate{\mach}{\pol}{\context} ~ \obs =
              (\mpcstate{\mach}{\pol}{\context},\obs) \machT\)}%
%
\judgment{\(\mathit{obs-forward} ~ \mpcstatename ~ \tau = \machT\)}
         {\(\mpcstatename \hookrightarrow \machT\)}

@@

\section{Simple Stack Safety, Formally}
\label{sec:sss}

@@

\[\ann \in \ANNS ::= \callmap + \retmap\]
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \FUNIDS \times \option{\ann}\]

@@

\definition Let \(\mpcstatename\) be a reachable state whose next instruction is annotated
as a call and whose call depth is \(\depth\). Let \(f ~ \mach ~ \context\) hold when \(\context = \_,\depth\),
and \(\components\) be the set of components \(\component\) such that
\(\sealcon ~ \pi_\mach(\mpcstatename) ~ \component\) holds. Then the {\em Call Rule} says that if
\(\mpcstatename \stepstocon \mpcstatename'\), it is sound to assume that
\(\mpcstatename' \hookrightarrow \MPCT | f\) and if \(\last(\MPCT) = \mach'\), then
\(\pi_\mach(\mpcstatename) ~ \component = \mach' ~ \component\).

@@

\subsection{Eager Confidentiality and the Transparency Rule}

@@

\definition Transparency Rule

@@

\section{Stack Safety with Sharing}

@@

\section{Coroutine Safety}

\subsection{Local State Encapsulation}
\label{sec:lse}

@@

Both the integrity and confidentiality components of local state
encapsulation concern themselves only with the accessibility of data,
and may still hold on a wide range of programs that violate expected
control flow. For instance, if {\tt f} managed to jump in the middle of
the code of {\tt g} with its call, confidentiality and integrity would
still be satisfied.
%
However, that is still unwanted behavior: for example, a caller (or a
callee) should not be able to bypass a password check by jumping (or
returning) in the middle of a block of code --- even if such an execution
would ostensibly satisfy local state encapsulation.
%
Stack safety enforcement mechanisms like \citet{Skorstengaard+19}
usually aim to prevent such unwanted flows: every jump between
functions should either be a call or a return, and each return should
be to the instruction after its corresponding call.

To formally capture this aspect of stack safety, we introduce three
security properties that rely on the underlying knowledge of the
program structure (call map $\callmap$, function map $\codemap$, return map $\retmap$, and entry
map $\entmap$): {\em control separation} ensures the validity of transition
sources between functions, {\em entry integrity} ensures the validity
of call targets, and {\em return integrity} ensures that of
return targets.

\definition%{Control Separation}
A system enjoys {\em control separation}
% with respect to a function map
%\(\codemap\), a call map \(\callmap\), and a return map \(\retmap\),
if, for any initial state \((\mach_0, \pol_0)\) and any adjacent pair of states
\(\mpostate{\mach_1}{\pol_1}{\obs_1}\) and \(\mpostate{\mach_2}{\pol_2}{\obs_2}\)
in the induced trace from \(\mpstate{\mach_0}{\pol_0}\),
if \(\codemap(\mach_1(\PCname)) \not = \codemap(\mach_2(\PCname))\),
then \(\mpstate{\mach_1}{\pol_1}\) is either a call \(\callmap(\mach_1(\PCname))\)
or a return \(\retmap(\mach_1(\PCname))\).

@@

\newcommand*{\Unmatched}{\mathit{um}}

Return integrity captures the expected behavior of marked returns with
respect to their call points. Intuitively, it says that the marked return
matching a call $\mach_c$ should satisfy $\ret{\mach_c}$.
Observe that, given an MP-trace $\mpstate{\mach_c}{\pol}\MPT$, if $\mach_c$ is
a call state then the matching return will be the first \emph{unmatched} return
in $\MPT$. So we begin by defining an auxiliary ``unmatched'' relation between
two traces.

\definition
We write $\Unmatched~\MPT~\MPT'$ if $\MPT'$ is
obtained from $\MPT$ by dropping elements until we reach the first unmatched return
(according to the return map).  Formally, $\Unmatched$ is defined coinductively as follows:
\begin{itemize}
\item A trace that starts with a return is related to itself:

\begin{center}
\begin{minipage}{.3\textwidth}
  \judgmenttwo{\(\callmap(\mach(\PCname)) = \bot\)}
              {\(\retmap(\mach(\PCname))\)}
              {\(\Unmatched ~ \mpstate{\mach}{\pol} ~ \mpstate{\mach}{\pol}\)}
\end{minipage}
\hspace*{0.1\textwidth}
\begin{minipage}{.3\textwidth}
  \judgmenttwo{\(\callmap(\mach(\PCname)) = \bot\)}
              {\(\retmap(\mach(\PCname))\)}
              {\(\Unmatched ~ \mpstate{\mach}{\pol}\MPT ~ \mpstate{\mach}{\pol}\MPT\)}
\end{minipage}
\end{center}

\item If a trace \(\MPT\) starts with a non-call, non-return state,
  its unmatched return must come later:

  \judgment{\(\callmap(\mach(\PCname)) = \bot
              \hspace{.5cm} \neg \retmap(\mach(\PCname))
              \hspace{.5cm}\Unmatched ~ \MPT ~ \MPT'\)}
           {\(\Unmatched ~ \mpstate{\mach}{\pol}\MPT ~ \MPT'\)}

\item Finally, if a trace starts with a call, then we must discard the first
  unmatched return from its tail to get to the real one:

  \judgmentbr{\(\callmap(\mach(\PCname)) = n \hspace{.5cm} \neg \retmap(\mach(\PCname)) \)}
             {\(\MPT = (m,p)\MPT_{\mathit{call}}\) \quad \(\Unmatched ~ \MPT_{\mathit{call}} ~ \MPT_{\mathit{matched}}\)}
             {\(\MPT_{\mathit{matched}} = \mpstate{\mach'}{\pol'} \MPT_{\mathit{tail}}\) \quad
              \(\Unmatched ~ \MPT_{\mathit{tail}} ~ \MPT_{\mathit{unmatched}}\)}
            {\(\Unmatched ~ \MPT ~ \MPT_{\mathit{unmatched}}\)}
\end{itemize}
\ifspace
\apt{Could cut formal definition for space.}
\fi

@@

\definition
  Given two machine states $\mach$ and $\mach'$ and a contour $\contour$, these
  satisfy the \emph{stack integrity test} if their high-integrity components
  match:
  \[
    \testInt{\contour}{\mach}{\mach'} \triangleq
    \forall \component . ~
    \contour(\component) = \HIGHINT \rightarrow
    \mach(\component) = \mach'(\component)
    \]
    \ifaftersubmission
\apt{We could have used this to define trace integrity in the first place...}
\fi
\definition Two machine states $\mach_1$ and $\mach_2$ satisfy the
\emph{stack confidentiality test} if the machines they stepped to
have their changed components coincide and the observations during
these steps are equal:
\[
\begin{array}{rl}
  \mathit{conf}_T ~ \mach_1 ~ \mach_2 ~ \triangleq &
  \exists \obs_1 ~ \obs_2 ~ \mach_1' ~ \mach_2'. ~
  \mach_1 \stepstoobs{\obs_1} \mach_1' \wedge \mach_2 \stepstoobs{\obs_2} \mach_2' \Rightarrow \\
&    \obs_1 = \obs_2 \wedge \forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1'(\component) = \mach_2'(\component)
\end{array}
\]
\ifaftersubmission
\apt{And the last clause here could have been used for trace confidentiality...}
\fi

@@

%%   \item
%% %
%%     If the machine takes a \emph{call step} and $\contour$ is the contour at
%%     the call then,
%% %
%%     (1) the variant stack test $\testVS{(\mach, \pol)}{\vs}$ must be
%%     satisfied,
%% %
%%     (2) the stack integrity test $\testInt{\contour}{\mach}{\mach'}$ is
%%     satisfied and the stack confidentiality test $\testConf{\mach}{\vm{\contour}}$
%%     is satisfied with resepct to an arbitrary $\contour$-variant
%%     of $\mach$,
%% =======
We also need two auxiliary notations that relate to variant stacks.
%
First, lockstep stack safety will check that the basic tests above hold for every
machine in the variant stack.  Given a machine that steps $(\mach,
\pol) \stepstopol{\obs} (\mach', \pol')$, say that a variant
stack $\vs$ satisfies the \emph{variant stack test} if for each
variant element $\vm{C}$ (which is a variation of $\mach$ for $C$),
$\vm{C}$ can take a step, denoted $\vm{C} \stepstoobs{\obs} \mach'$,
while satisfying the stack integrity test $\testInt{C}{\mach}{\mach'}$
and stack confidentiality test $\testConf{\mach}{\mach'}$ with regard
to the original machine state. We will write $\testVS{(\mach,
  \pol)}{\vs}$ for this compound check.
%\apt{I'm having trouble here and below with
%  the scoping of $C$. Each variant stack is for one particular $C$, right?
%  So why not write $vs_C$ rather than $vm_C$ ?}
% LEO: Each machine has its own contour. Clarified above, hopefully
%% >>>>>>> 1886f7a7bf858ce0c9518e407d9481518a4f028d
%
Second, we will write $\vs \stepsto \vs'$ if every variant machine
in $\vs$ steps to the corresponding machine in $\vs'$.
%

@@

\item
  If the machine takes a \emph{call step} and $\contour$ is the contour at
  the call
  %% \rb{Corrected the step function here, or should it be
  %% $\hookrightarrow$ and give the rest of the induced trace?}
  \[(\mach, \pol) \stepstopol{\obs} (\mach', \pol') \wedge \callmap(\mach) = n,\]
%
  then the variant stack test must be
  satisfied
  \[\testVS{(\mach, \pol)}{\vs},\]
%
%    (2) the stack integrity test $\testInt{\contour}{\mach}{\mach'}$ is
%    satisfied and the stack confidentiality test $\testConf{\mach}{\vm{\contour}}$
%    is satisfied with regard to an arbitrary $\contour$-variant
%    of $\mach$,
%
  and trace lockstep stack safety must be coinductively satisfied
  for the remainder of the trace and for every variant stack
  that is the result of adding a variation of $\mach'$ with
  respect to $C$ at the top of the stack $\vs'$ that $\vs$ steps
  to:
  \[\testProp{}{((\mach', \pol', \obs)\MPT)}{(\vm{\contour} : \vs')}\]

\item
%
  If the machine $\mach$ takes a \emph{return step},
  \[(\mach, \pol) \stepstopol{\obs} (\mach', \pol') \wedge \retmap(\mach),\]
  %
  then the top of the variant stack also returns,
  the tail of $\vs$ satisfies the stack safety test
  \[\testVS{(\mach, \pol)}{\mathit{tail}(\vs)},\]
  %
  and trace lockstep stack safety must be coinductively satisfied for
  the remainder of the trace and for the tail of the variant stack
  that $\vs$ steps to:
  \[\testProp{}{((\mach', \pol', \obs)\MPT)}{(\mathit{tail}(\vs'))}\]

>>>>

Alongside integrity, we have {\em confidentiality}, in which callers' data is protected
from leakage by their callees. Consider the first example in figure \ref{fig:confexamples},
in which {\tt main} recieves a key, then calls {\tt f}. If {\tt f} is an untrusted function,
it would be bad if it could just read {\tt key}. But there are more subtle examples,
such as the second one, where a secret value controls which function of {\tt g} and
{\tt h} are called prior to calling {\tt f}. Here, if {\tt g} or {\tt h} leaves behind
identifying information in unused stack space, {\tt f} could still deduce information
about the secret. So our confidentiality properties also support a {\em insensitivity rule},
that each function's behavior is independent of the state of its caller, other than arguments.
This also makes it easier, though not trivial, to prove idempotence: the channels through
which a callee can remember its own history are limited to those outside the stack.

@@

The step function of the machine takes a machine state and produces a
pair of a machine state and an {\em observation}, which may be either
silent (written \(\tau\)) or a word of data\ifaftersubmission\bcp{This is a rather concrete
  choice!  Why not leave the set of observations abstract?}\fi that the machine
communicates to the outside world:
%
\[\obs \in \OBSS = \{\tau\} \uplus \WORDS\]
\[\mach \stepstoobs[\obs] \mach' \in \MACHS \rightarrow \MACHS \times \OBSS \]
%
This step function is total, so the machine's execution traces
(defined in \cref{sec:traces}) are infinite.

@@

\judgmenttwo{\(\mach \stepstoobs[\obs] \mach'\)}{\((\mach, \pol)
               \polstep \pol'\)}
            {\(\mpstate{\mach}{\pol} \stepstopol[\obs]
               \mpstate{\mach'}{\pol'}\)}

@@

The ``trace-of'' operator, written \(\mach \hookrightarrow \machT\),
coinductively relates a machine state with the trace of machine states
and observations produced by repeated application of step. It's defined in
terms of a coinductive helper, \(\mathit{obsforward}\):

\judgmenttwo{\(\mach \stepstoobs[\obs'] \mach'\)}
            {\(\mathit{obsforward} ~ \mach' ~ \obs' = \machT\)}
            {\(\mathit{obsforward} ~ \mach ~ \obs = (\mach,\obs) \machT\)}%
%
\judgment{\(\mathit{obsforward} ~ \mach ~ \tau = \machT\)}
         {\(\mach \hookrightarrow \machT\)}
\noindent
(We use juxtaposition of an element and a sequence to represent ``cons.'')
Since the step function is total, if \(\mach \hookrightarrow \machT\),
then \(\machT\) must be infinite.

@@

\judgment{\(\neg \exists \pol' . \mpcstate{\mach}{\pol} \polstep \pol'\)}
         {\(\mathit{obsforward} ~ \mpcstate{\mach}{\pol}{\context} ~ \obs =
           \mpcstate{\mach}{\pol}{\context},\obs\)}
%
\judgmenttwo{\(\mpcstate{\mach}{\pol}{\context} \stepstoobs[\obs'] \mpcstate{\mach'}{\pol'}{\context'}\)}
            {\(\mathit{obsforward} ~ \mpcstate{\mach'}{\pol'}{\context'} ~ \obs' = \machT\)}
            {\(\mathit{obsforward} ~ \mpcstate{\mach}{\pol}{\context} ~ \obs =
              (\mpcstate{\mach}{\pol}{\context},\obs) \machT\)}%
%
\judgment{\(\mathit{obsforward} ~ \mpcstatename ~ \tau = \machT\)}
         {\(\mpcstatename \hookrightarrow \machT\)}

@@

\section{Local State Encapsulation, Formally}
\label{sec:lse}

@@

\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap\})\]
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \FUNIDS \times \option{\ann}\]

@@

\definition Let \(\mpcstatename\) be a reachable state whose PC value is annotated
as a call and whose call depth is \(\depth\). Assume \(\mpcstatename \stepstocon \mpcstatename'\).
Let \(\MPCT\) be the trace ending after the corresponding return, if any, defined by
\(\mpcstatename' \hookrightarrow \MPCT | f\) with \(f ~ \mach ~ \context\) holding when
\(\context = \_,\depth\). Finally let \(\components\) be the set of components \(\component\)
such that \(\sealcon ~ \pi_\mach(\mpcstatename) ~ \component\) holds. Then by the {\em Call Rule},
it is sound to assume that if \(\last(\pi_\mach(\MPCT)) = \mach'\), then
\(\pi_\mach(\mpcstatename) ~ \component = \mach' ~ \component\).

@@

\subsection{Eager Confidentiality and the Insensitivity Rule}

@@

\definition Let \(\mpcstatename\) be a reachable call state. Assume the that the call is successful
and \(\mpcstatename \stepstocon \mpcstatename'\). Then let \(\npcstatename'\) be a \(\components\)-variant
where \(\components\) is the set of all addresses in the stack. Then by the {\em Insensitivity Rule},
if the trace from \(\mpcstatename'\) eventually returns, so does that from \(\npcstatename'\),
their states after the return have the same differences, and up to return their traces are observationally
equivalent.

@@

\subsection{Stack Safety with Sharing}
\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

\subsection{Local State Encapsulation}

\definition A system enjoys {\em local state encapsulation} if it enjoys eager integrity and
eager confidentiality.

\definition A system enjoys {\em lazy local state encapsulation} if it enjoys lazy integrity
and eager confidentiality.

We do not give a confidentiality equivalent to lazy integrity, because the family of lazy
enforcement mechanisms that we consider under the HOPE system in fact enforce eager confidentiality.
A policy based on taint-tracking might require such a lazy confidentiality, and it would be constructed
by replacing the ``same-difference'' condition with one that requires any differences to produce
observationally equivalent states. But for our purposes it is irrelevant.

\section{Coroutine Safety}
\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap, \yieldmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

@@

Both the integrity and confidentiality components of local state
encapsulation concern themselves only with the accessibility of data,
and may still hold on a wide range of programs that violate expected
control flow. The archetypal example of this is the {\em awkward example},
in which an adversarial callee stores a return address and returns to it
on a subsequent call, thus violating the expected control flow of the
caller without actually violating the caller's integrity. But it also
encompasses simpler violations, such as a function bypassing a password
check by jumping (or returning) in the middle of a block of code.
%
Stack safety enforcement mechanisms like \citet{Skorstengaard+19}
usually aim to prevent such unwanted flows: every jump between
functions should either be a call or a return, and each return should
be to the instruction after its corresponding call.

To formally capture this aspect of stack safety, we introduce some more
security properties. {\em Control separation} restricts transitions between
functions to follow the interfaces set out by call, return, and yield, forming
a foundation for all of the other properties that rely on those interfaces for
meaning. {\em Entry integrity} ensures the validity of call targets,
{\em return integrity} ensures that of return targets, and
{\em yield-back integrity} ensures that of yield targets.

Recall that our properties use a compiler-derived code-map determine
which addresses are instructions and which functions they belong to, as well
as annotating them as calls, returns, and yields, as well as sharing information.
We now extend it with an annotation for valid entry points:
\[\ann \in \ANNS ::= \mathscr{P}(\{\callmap, \retmap, \yieldmap, \entrymap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

\definition%{Control Separation}
A system enjoys {\em control separation} when each reachable step \(\mpcstatename\)
where 
% with respect to a function map
%\(\codemap\), a call map \(\callmap\), and a return map \(\retmap\),
if, for any initial state \((\mach_0, \pol_0)\) and any adjacent pair of states
\(\mpostate{\mach_1}{\pol_1}{\obs_1}\) and \(\mpostate{\mach_2}{\pol_2}{\obs_2}\)
in the induced trace from \(\mpstate{\mach_0}{\pol_0}\),
if \(\codemap(\mach_1(\PCname)) \not = \codemap(\mach_2(\PCname))\),
then \(\mpstate{\mach_1}{\pol_1}\) is either a call \(\callmap(\mach_1(\PCname))\)
or a return \(\retmap(\mach_1(\PCname))\).

@@

@@

\definition
  Given two machine states $\mach$ and $\mach'$ and a contour $\contour$, these
  satisfy the \emph{stack integrity test} if their high-integrity components
  match:
  \[
    \testInt{\contour}{\mach}{\mach'} \triangleq
    \forall \component . ~
    \contour(\component) = \HIGHINT \rightarrow
    \mach(\component) = \mach'(\component)
    \]
    \ifaftersubmission
\apt{We could have used this to define trace integrity in the first place...}
\fi
\definition Two machine states $\mach_1$ and $\mach_2$ satisfy the
\emph{stack confidentiality test} if the machines they stepped to
have their changed components coincide and the observations during
these steps are equal:
\[
\begin{array}{rl}
  \mathit{conf}_T ~ \mach_1 ~ \mach_2 ~ \triangleq &
  \exists \obs_1 ~ \obs_2 ~ \mach_1' ~ \mach_2'. ~
  \mach_1 \stepstoobs[\obs_1] \mach_1' \wedge \mach_2 \stepstoobs[\obs_2] \mach_2' \Rightarrow \\
&    \obs_1 = \obs_2 \wedge \forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1'(\component) = \mach_2'(\component)
\end{array}
\]
\ifaftersubmission
\apt{And the last clause here could have been used for trace confidentiality...}
\fi

@@

%%   \item
%% %
%%     If the machine takes a \emph{call step} and $\contour$ is the contour at
%%     the call then,
%% %
%%     (1) the variant stack test $\testVS{(\mach, \pol)}{\vs}$ must be
%%     satisfied,
%% %
%%     (2) the stack integrity test $\testInt{\contour}{\mach}{\mach'}$ is
%%     satisfied and the stack confidentiality test $\testConf{\mach}{\vm{\contour}}$
%%     is satisfied with resepct to an arbitrary $\contour$-variant
%%     of $\mach$,
%% =======
We also need two auxiliary notations that relate to variant stacks.
%
First, lockstep stack safety will check that the basic tests above hold for every
machine in the variant stack.  Given a machine that steps $(\mach,
\pol) \stepstopol[\obs] (\mach', \pol')$, say that a variant
stack $\vs$ satisfies the \emph{variant stack test} if for each
variant element $\vm{C}$ (which is a variation of $\mach$ for $C$),
$\vm{C}$ can take a step, denoted \(\vm{C} \stepstoobs[\obs] \mach'\),
while satisfying the stack integrity test \(\testInt{C}{\mach}{\mach'}\)
and stack confidentiality test $\testConf{\mach}{\mach'}$ with regard
to the original machine state. We will write $\testVS{(\mach,
  \pol)}{\vs}$ for this compound check.
%\apt{I'm having trouble here and below with
%  the scoping of $C$. Each variant stack is for one particular $C$, right?
%  So why not write $vs_C$ rather than $vm_C$ ?}
% LEO: Each machine has its own contour. Clarified above, hopefully
%% >>>>>>> 1886f7a7bf858ce0c9518e407d9481518a4f028d
%
Second, we will write $\vs \stepsto \vs'$ if every variant machine
in $\vs$ steps to the corresponding machine in $\vs'$.
%

@@

\item
  If the machine takes a \emph{call step} and $\contour$ is the contour at
  the call
  %% \rb{Corrected the step function here, or should it be
  %% $\hookrightarrow$ and give the rest of the induced trace?}
  \[(\mach, \pol) \stepstopol[\obs] (\mach', \pol') \wedge \callmap(\mach) = n,\]
%
  then the variant stack test must be
  satisfied
  \[\testVS{(\mach, \pol)}{\vs},\]
%
%    (2) the stack integrity test $\testInt{\contour}{\mach}{\mach'}$ is
%    satisfied and the stack confidentiality test $\testConf{\mach}{\vm{\contour}}$
%    is satisfied with regard to an arbitrary $\contour$-variant
%    of $\mach$,
%
  and trace lockstep stack safety must be coinductively satisfied
  for the remainder of the trace and for every variant stack
  that is the result of adding a variation of $\mach'$ with
  respect to $C$ at the top of the stack $\vs'$ that $\vs$ steps
  to:
  \[\testProp{}{((\mach', \pol', \obs)\MPT)}{(\vm{\contour} : \vs')}\]

\item
%
  If the machine $\mach$ takes a \emph{return step},
  \[(\mach, \pol) \stepstopol[\obs] (\mach', \pol') \wedge \retmap(\mach),\]
  %
  then the top of the variant stack also returns,
  the tail of $\vs$ satisfies the stack safety test
  \[\testVS{(\mach, \pol)}{\mathit{tail}(\vs)},\]
  %
  and trace lockstep stack safety must be coinductively satisfied for
  the remainder of the trace and for the tail of the variant stack
  that $\vs$ steps to:
  \[\testProp{}{((\mach', \pol', \obs)\MPT)}{(\mathit{tail}(\vs'))}\]
